We Are All Trying to Describe Something And We Don't Have the Words

### 2023-04-17 outputs/paper/paper.qmd
digging deeper into danceability variable

This cannot be the right formula. $$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)} = \frac{1}{1 + e^{-(\beta_0 + \beta_1 x_1 + \cdots + \beta_p x_p)}}
$$ {#eq-bayes}

@@

@@

@@

According to this model, though, danceability is the most important feature in predicting whether or not a song was produced by Jack Antonoff. This is so hilarious. This was a feature that was invented in a lab 15 years ago. This number refers to the time a bunch of undergraduates were paid (hopefully?) to listen to a bunch of songs and tag whether they were danceable or not. It captures this je-ne-sais-quoi essence of music that connects with listeners on a visceral level. Even if it doesn't make YOUR body want to move, you could imagine it making SOMEBODY'S body want to move.

But does Jack Antonoff's music even make your body want to move? Let's put a pin in that.

Eliciting a visceral reaction doesn't cause career success -- factors in a career trajectory like network, connections, right time right place ism and other elements of biography all shape that sort of thing.

>>>>

\[add the formula\]

@@

data_reduced <- read.csv(here::here("inputs/data/data_reduced.csv"))

@@

0.743 accuracy, 0.841 roc_auc. Interesting. Check it out:

```{r}
#jackmatrix
```

data_reduced |> 
  pivot_longer(cols = c(danceability, energy, loudness, mode,
               speechiness, acousticness, instrumentalness, liveness, valence,
               tempo),
               names_to = "name",
               values_to = "value"
  ) |> 
  ggplot(aes(x = value, color = jack)) +
  stat_ecdf() +
  facet_wrap(vars(name), 
             nrow = 3, 
             ncol = 4,
             scales = "free") +
  theme_minimal() +
  labs(
    x = "Value",
    y = "Proportion"
  )

And here are the different variables' importance on determining whether a song was had any Antonoff involvement.

jack_vip <- read.csv(here::here("inputs/data/jack_vip.csv"))

jack_vip |>
   knitr::kable(
     col.names = c("Variable", 
                   "Importance",
                   "Sign")
  )

jack_vip %>%
  group_by(Sign) %>%
  slice_max(Importance, n = 15) %>%
  ungroup() %>%
  ggplot(aes(Importance, fct_reorder(Variable, Importance), fill = Sign)) + 
  geom_col() +
  facet_wrap(vars(Sign), scales = "free_y") +
  labs(y = NULL) +
  theme(legend.position = "none")
```

Danceability, with a score of 4.32, had the highest level of importance in determining whether or not a song was produced or co-produced by Jack Antonoff.

@@

According to this model, though, danceability is the most important feature in predicting whether or not a song was produced by Jack Antonoff. This is so hilarious. This was a feature that was invented in a lab 15 years ago. This number refers to the time a bunch of undergraduates were paid (hopefully?) to listen to a bunch of songs and tag whether they were danceable or not. It is pretty much based on intuition. It captures this je-ne-sais-quoi essence of music that connects with listeners on a visceral level. Even if it doesn't make YOUR body want to move, you could imagine it making SOMEBODY'S body want to move.

library(tidyverse)

df %>%
  filter(jack == 1) %>%
  arrange(desc(danceability)) |>
  distinct(track_name, .keep_all = TRUE) |>
  select(artist_name, danceability, track_name) |>
  knitr::kable(
     col.names = c("Artist Name", 
                   "Danceability",
                   "Track")
  )

### What do I think:

-   I Think He Knows by Taylor Swift:

    -   pretty danceable tbh

-   Vigilante Shit by Taylor Swift:

    -   Not danceable. But it is trying to coerce you into some sort of body feeling.

-   Heaven is Here by Florence and the Machine

    -   DEFINITELY not danceable. But it is trying to get your body to do something. Kind of sounds like it's suggesting that you join a Macedonian phalanx or something. But no. Not danceable.

    ![](images/Macefonian_phalanx.png)

-   I Wanna Get Better by Bleachers

    -   I don't know if "danceability" is the word, but I'll give it "anthem"-y. Like, I can't picture a group of friends dancing to this in the kitchen, but I can picture someone listening to it in their car when it comes on the radio on their way to give a presentation or negotiate a promotion or something.

-   Cornelia Street by Taylor Swift

    -   Yeah I'm dancing. Or at least bobbing my head.

```{r}
#| echo: false
#| warning: false
library(dplyr)
library(ggplot2)

df %>%
  filter(jack == 1) %>%
  count(artist_name) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  ggplot(aes(x = reorder(artist_name, n), y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Artists with Most Jack = 1 Values", x = "Artist", y = "Count")

df |>
  arrange(desc(danceability)) |>
  select(artist_name, danceability, track_name)
